---
title: "R Notebook"
output: html_notebook
---

# TOC of Regressions and Visualizations
1. [Libraries](#libraries)
2. [Directory Setup](#dir)
3. [Pooled OLS](#pooled)
4. [Random Effects](#rnd_eff)
5. [Fixed Effects + Time-Fixed Effects](#fxd_eff)
6. [Hausman Test](#haus)
7. [Multicollinearity](#multicollinearity)
8. [Additional Tests for Significance](#add_tests)

# Libraries <a name = 'libraries'></a>
```{r}
library(tidyverse)
library(stargazer)
library(varhandle)
library(plm)
library(lmtest)
library(sandwich)
library(broom)
library(rstudioapi)
library(corrplot)
library('Hmisc')
library('car')
library(glue)
```

# Directory Setup <a name = "dir"></a>

```{r}
current_path <- getSourceEditorContext()$path
current_directory <- strsplit(current_path, '/')[[1]][1:length(strsplit(current_path, '/')[[1]]) - 1]
current_directory <- paste(as.character(current_directory), collapse = '/')
current_directory

get_file_path <- function(path) {
  return(paste(current_directory, path, sep="/"))
}

trade_and_the_se_df <- read.csv(get_file_path('trade_and_the_se.csv'))
trade_and_the_se_df$tax_burden <- factor(trade_and_the_se_df$tax_burden) # For not having tax_burden as a factor
trade_and_the_se_df$tax_burden <- unfactor(trade_and_the_se_df$tax_burden) 

options(scipen=999)
```

# Preliminaries <a name = 'pre'></a>
```{r}
indep_vars <- c('trade_tax', 'applied_tariff_rate', 'exports_per_cap', 'imports_per_cap', 'wa_rca')
control_vars <- c('composite_wgi', 'gdp_per_cap', 'income_tax', 'vat_tax', 'tax_burden')

form_wo_controls <- se_size ~ trade_tax + applied_tariff_rate + exports_per_cap + imports_per_cap + wa_rca
form_with_controls <- se_size ~ trade_tax + applied_tariff_rate + exports_per_cap + imports_per_cap + wa_rca + 
                  composite_wgi + gdp_per_cap + income_tax + vat_tax + tax_burden
```

# Pooled OLS <a name = 'pooled'></a>
```{r}
# w/o control variables
pooled_ols_wo_controls <- lm(form_wo_controls, data = trade_and_the_se_df)
print('W/O CONTROLS')
coeftest(pooled_ols_wo_controls, vcov = vcovHC(pooled_ols_wo_controls, type = "HC0"))
# summary(pooled_ols_wo_controls)
# stargazer(pooled_ols_wo_controls, type = "text")

# w/ control variables
pooled_ols_with_controls <- lm(form_wo_controls, data = trade_and_the_se_df)
print('W CONTROLS')
coeftest(pooled_ols_with_controls, vcov = vcovHC(pooled_ols_with_controls, type = "HC0"))
# summary(pooled_ols_with_controls)
# stargazer(pooled_ols_with_controls, type = "text")
```

# Random Effects <a name = 'rnd_eff'></a>
```{r}
random_effects_wo_controls <- plm(form_wo_controls, data = trade_and_the_se_df, model = 'random')
coeftest(random_effects_wo_controls, vcov = vcovHC(random_effects_wo_controls, type = "HC0"))
# summary(random_effects_wo_controls)
# stargazer(random_effects_wo_controls, type = "text")


random_effects_with_controls <- plm(form_with_controls, data = trade_and_the_se_df, model = 'random')
coeftest(random_effects_with_controls, vcov = vcovHC(random_effects_with_controls, type = "HC0"))
# summary(random_effects_with_controls)
# stargazer(random_effects_with_controls, type = "text")
```

# Fixed Effects + Time-Fixed Effects <a name = 'fxd_eff'></a>
```{r}
fixed_effects_wo_controls <- plm(form_wo_controls, data = trade_and_the_se_df, model = 'within')
coeftest(fixed_effects_wo_controls, vcov = vcovHC(fixed_effects_wo_controls, type = "HC0"))
# summary(fixed_effects_wo_controls)
# stargazer(fixed_effects_wo_controls, type = "text")

fixed_effects_with_controls <- plm(form_with_controls, data = trade_and_the_se_df, model = 'within')
coeftest(fixed_effects_with_controls, vcov = vcovHC(fixed_effects_with_controls, type = "HC0"))
# summary(fixed_effects_with_controls)
# stargazer(fixed_effects_with_controls, type = "text")
```
Time-Fixed Effects
```{r}
trade_and_the_se_df_with_year_dummies <- cbind(trade_and_the_se_df, as.data.frame.matrix(table(sequence(nrow(trade_and_the_se_df)), trade_and_the_se_df$year)))

for (i in 14:ncol(trade_and_the_se_df_with_year_dummies)) {
  colnames(trade_and_the_se_df_with_year_dummies)[i] <- paste('X', 2000 - 14 + i, sep = "")
}

year_dummies <- lapply(as.list(2001:2015), function(x) paste('X', x, sep = ""))
time_dummies_no_controls_factors <- c(indep_vars, year_dummies)
time_dummies_with_controls_factors <- c(indep_vars, control_vars, year_dummies)
form_wo_controls_and_year_dummies <- as.formula(paste("se_size~", paste(time_dummies_no_controls_factors, collapse="+")))
form_w_controls_and_year_dummies <- as.formula(paste("se_size~", paste(time_dummies_with_controls_factors, collapse="+")))

time_fixed_effects_wo_controls <- plm(form_wo_controls_and_year_dummies, data = trade_and_the_se_df_with_year_dummies, model = 'within')
coeftest(time_fixed_effects_wo_controls, vcov = vcovHC(time_fixed_effects_wo_controls, type = "HC0"))

time_fixed_effects_w_controls <- plm(form_w_controls_and_year_dummies, data = trade_and_the_se_df_with_year_dummies, model = 'within')
coeftest(time_fixed_effects_w_controls, vcov = vcovHC(time_fixed_effects_w_controls, type = "HC0"))
```

# Hausman Test <a name = 'haus'></a>
```{r}
phtest(fixed_effects_with_controls, random_effects_with_controls)
```

# Multicollinearity <a name = 'multicollinearity'></a>
Correlation Matrix

Function by Paul van der Laken \
https://www.r-bloggers.com/2020/07/create-a-publication-ready-correlation-matrix-with-significance-levels-in-r
```{r}
correlation_matrix <- function(df, 
                               type = "pearson",
                               digits = 3, 
                               decimal.mark = ".",
                               use = "all", 
                               show_significance = TRUE, 
                               replace_diagonal = FALSE, 
                               replacement = ""){
  
  # check arguments
  stopifnot({
    is.numeric(digits)
    digits >= 0
    use %in% c("all", "upper", "lower")
    is.logical(replace_diagonal)
    is.logical(show_significance)
    is.character(replacement)
  })
  # we need the Hmisc package for this
  require(Hmisc)
  
  # retain only numeric and boolean columns
  isNumericOrBoolean = vapply(df, function(x) is.numeric(x) | is.logical(x), logical(1))
  if (sum(!isNumericOrBoolean) > 0) {
    cat('Dropping non-numeric/-boolean column(s):', paste(names(isNumericOrBoolean)[!isNumericOrBoolean], collapse = ', '), '\n\n')
  }
  df = df[isNumericOrBoolean]
  
  # transform input data frame to matrix
  x <- as.matrix(df)
  
  # run correlation analysis using Hmisc package
  correlation_matrix <- Hmisc::rcorr(x, type = )
  R <- correlation_matrix$r # Matrix of correlation coeficients
  p <- correlation_matrix$P # Matrix of p-value 
  
  # transform correlations to specific character format
  Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)
  
  # if there are any negative numbers, we want to put a space before the positives to align all
  if (sum(R < 0) > 0) {
    Rformatted = ifelse(R > 0, paste0(' ', Rformatted), Rformatted)
  }
  
  # add significance levels if desired
  if (show_significance) {
    # define notions for significance levels; spacing is important.
    stars <- ifelse(is.na(p), "   ", ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "*  ", "   "))))
    Rformatted = paste0(Rformatted, stars)
  }
  # build a new matrix that includes the formatted correlations and their significance stars
  Rnew <- matrix(Rformatted, ncol = ncol(x))
  rownames(Rnew) <- colnames(x)
  colnames(Rnew) <- paste(colnames(x), "", sep =" ")
  
  # replace undesired values
  if (use == 'upper') {
    Rnew[lower.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (use == 'lower') {
    Rnew[upper.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (replace_diagonal) {
    diag(Rnew) <- replacement
  }
  
  return(Rnew)
}

save_correlation_matrix = function(df, filename, ...) {
  write.csv2(correlation_matrix(df, ...), file = filename)
}
```

```{r}
trade_and_the_se_df_numeric <- sapply(trade_and_the_se_df %>% select(-c('code', 'year')), as.numeric)
# colnames(trade_and_the_se_df_numeric) <- c('')
cor_data = cor(trade_and_the_se_df_numeric)
corrplot(cor_data, method="number", number.cex = 0.7, tl.cex = 0.7, diag = F, tl.col = 'black')
correlation_matrix(trade_and_the_se_df)
save_correlation_matrix(trade_and_the_se_df, filename = get_file_path('correlation_matrix_1'))
# Put the one with significance codes in the appendix or side-by-side
```
VIFs
```{r}
vif_values <- vif(lm(form_w_controls_and_year_dummies, data = trade_and_the_se_df_with_year_dummies))
vif_values
```

# Additional Tests for Signficance <a name = 'add_tests'></a>
Joint significance of imports and exports
$$
F_{stat} = \frac {(SSR_r - SSR_{ur})/q} {SSR_{ur} / (n - k - 1)}
$$

F-stat for imports and exports
```{r}
form_w_controls_and_year_dummies_no_imports_exports <- as.formula(paste("se_size~", paste(setdiff(time_dummies_with_controls_factors, c('exports_per_cap', 'imports_per_cap')), collapse="+")))
form_w_controls_and_year_dummies_no_imports_exports

time_fixed_effects_w_controls_no_imports_exports <- plm(form_w_controls_and_year_dummies_no_imports_exports, data = trade_and_the_se_df_with_year_dummies, model = 'within')
# coeftest(time_fixed_effects_w_controls_no_imports_exports, vcov = vcovHC(time_fixed_effects_w_controls_no_imports_exports, type = "HC0"))
# summary(time_fixed_effects_w_controls_no_imports_exports)

SSR_r <- deviance(time_fixed_effects_w_controls_no_imports_exports)
SSR_ur <- deviance(time_fixed_effects_w_controls)
n = 1234; k = length(time_dummies_with_controls_factors) # Do I include the year dummies?
q = 2

f_stat <- ((SSR_r - SSR_ur) / q) * ((n - k - 1) / SSR_ur)
f_stat

probability_of_f_stat <- pf(f_stat, q, n - k - 1, lower.tail = F)
sig_15 <- qf(0.15, q, n - k - 1, lower.tail = F)
sig_10 <- qf(0.1, q, n - k - 1, lower.tail = F)
sig_05 <- qf(0.05, q, n - k - 1, lower.tail = F)
sig_01 <- qf(0.01, q, n - k - 1, lower.tail = F)
print(glue('F_stat = {round(f_stat, 3)} ({round(probability_of_f_stat, 4) * 100}%); {round(sig_15, 4)}, {round(sig_10, 4)}, {round(sig_05, 4)}, {round(sig_01, 4)}'))
```
Imports and Exports are Jointly non-significant

F-stat for Taxes on Goods and Services Tax and Tax Burden
```{r}
form_w_controls_and_year_dummies_no_burden_vat <- as.formula(paste("se_size~", paste(setdiff(time_dummies_with_controls_factors, c('tax_burden', 'vat_taxes')), collapse="+")))
form_w_controls_and_year_dummies_no_burden_vat

time_fixed_effects_w_controls_no_burden_vat <- plm(form_w_controls_and_year_dummies_no_burden_vat, data = trade_and_the_se_df_with_year_dummies, model = 'within')
# coeftest(time_fixed_effects_w_controls_no_imports_exports, vcov = vcovHC(time_fixed_effects_w_controls_no_imports_exports, type = "HC0"))
# summary(time_fixed_effects_w_controls_no_imports_exports)

SSR_r <- deviance(time_fixed_effects_w_controls_no_burden_vat)
SSR_ur <- deviance(time_fixed_effects_w_controls)

f_stat <- ((SSR_r - SSR_ur) / q) * ((n - k - 1) / SSR_ur)
f_stat

probability_of_f_stat <- pf(f_stat, q, n - k - 1, lower.tail = F)
print(glue('F_stat = {round(f_stat, 3)} ({round(probability_of_f_stat, 4) * 100}%); {round(sig_15, 4)}, {round(sig_10, 4)}, {round(sig_05, 4)}, {round(sig_01, 4)}'))
```
