---
title: "R Notebook"
output: html_notebook
---

# TOC of Data Cleaning

1.  [Libraries](#libraries)
2.  [Directory Setup](#dir)
3.  [Weighted Average Revealed Competitive Advantage Index](#wa_rca)
4.  [Working with the Country Names](#country_names)
5.  [Changing the Strucutre of the Data to Panel](#panel) \
  5.1 [Dependent Variable](#dep_var) \
  5.2 [Preliminaries](#pre_var) \
  5.3 [Independent Variables](#indep_var) \
  5.4 [Control Variables](#con_var)
6.  [Scaling and Alterations](#alters)
7.  [Checking Datasets](#checking)
8.  [Filtering and Combining Data](#filtering)
9.  [Interpolation and Final Cleaning](#interpolating)
10. [Exporting the Dataset](#exporting)

# Libraries <a name="libraries"></a> {#libraries}

```{r, results = 'hide', warnings = FALSE}
library(tidyverse)
library(readxl)
library(glue)
library(purrr)
library(roll)
library(zoo)
library(stargazer)
library(varhandle)
library(plm)
library(lmtest)
library(sandwich)
library(broom)
library(rstudioapi)
library(Hmisc)
```

# Directory Setup <a name = "dir"></a>

```{r}
current_path <- getSourceEditorContext()$path
current_directory <- strsplit(current_path, '/')[[1]][1:length(strsplit(current_path, '/')[[1]]) - 1]
current_directory <- paste(as.character(current_directory), collapse = '/')
current_directory

get_file_path <- function(path) {
  return(paste(current_directory, path, sep="/"))
}
```

# Weighted Average Revealed Competitive Advantage Index <a name = "wa_rca"></a>
Getting all WITS Files
```{r}
wits_files <- list.files(path = get_file_path("Data/WITS/EXP"), pattern="*.csv", full.names=TRUE, recursive=FALSE)
wits_rca_files <- list.files(path = get_file_path("Data/WITS/RCA"), pattern="*.csv", full.names=TRUE, recursive=FALSE)
all_wits_tibbles = wits_files %>% map( ~read_csv(.x))
all_rca_tibbles = wits_rca_files %>% map( ~read_csv(.x))
```

Finding Countries that don't exist in all datasets
```{r}
first_tibble = all_wits_tibbles[[1]]
original_countries <- data.frame(first_tibble)$country
print(original_countries)

find_inconsistent_nations <- function(list_of_tibbles) {
  all_to_remove = ''
  
  for (i in 2:length(list_of_tibbles)) {
    
    b <- 1; j <- 1;  # b -> original; l -> current_check
    
    current_tibble = list_of_tibbles[[i]]
    while(j <= length(data.frame(current_tibble)$country) && b <= length(data.frame(first_tibble)$country)) {
      
      if (data.frame(first_tibble)$country[b] != data.frame(current_tibble)$country[j]) {
        
        if (data.frame(first_tibble)$country[b + 1] == data.frame(current_tibble)$country[j]) {
          j <- j - 1;
          all_to_remove = paste(all_to_remove, data.frame(first_tibble)$country[b], sep = ':')
          # print(glue('- {data.frame(list_of_tibbles[1])$country[b]}'));
        } else if (data.frame(first_tibble)$country[b] == data.frame(current_tibble)$country[j + 1]) {
          b <- b - 1 
          all_to_remove = paste(all_to_remove, data.frame(current_tibble)$country[j], sep = ':')
          # print(glue('+ {data.frame(list_of_tibbles[i])$country[j]}'));
        } else {
          print('Double Issue. Investigate Further'); break;
        }
      }; j <- j + 1; b <- b + 1
      
    }
  }
  countries_to_remove <- as.list(unlist(strsplit(all_to_remove, ':')))
  return(countries_to_remove)
}
```
Filtering out all countries to remove
```{r}
countries_to_remove <- find_inconsistent_nations(all_wits_tibbles)
countries_to_remove <- unique(unlist(countries_to_remove, use.names = FALSE))
countries_to_remove <- countries_to_remove[2:length(countries_to_remove)]

rca_countries_to_remove <- find_inconsistent_nations(all_rca_tibbles)
rca_countries_to_remove <- unique(unlist(rca_countries_to_remove, use.names = FALSE))
rca_countries_to_remove <- rca_countries_to_remove[2:length(rca_countries_to_remove)]

all_countries_to_remove = unique(c(countries_to_remove, rca_countries_to_remove))

all_wits_tibbles_binded <- bind_rows(all_wits_tibbles)
all_rca_tibbles_binded <- bind_rows(all_rca_tibbles)

colnames(all_wits_tibbles_binded)[1] <- 'reporter_name'
colnames(all_wits_tibbles_binded)[2] <- 'partner_name'
colnames(all_wits_tibbles_binded)[3] <- 'trade_flow'
colnames(all_wits_tibbles_binded)[4] <- 'product_group'
colnames(all_wits_tibbles_binded)[5] <- 'indicator'
colnames(all_rca_tibbles_binded)[1] <- 'reporter_name'
colnames(all_rca_tibbles_binded)[2] <- 'partner_name'
colnames(all_rca_tibbles_binded)[3] <- 'trade_flow'
colnames(all_rca_tibbles_binded)[4] <- 'product_group'
colnames(all_rca_tibbles_binded)[5] <- 'indicator'

all_wits_tibbles_binded_wo_removing_countries <- all_wits_tibbles_binded %>% 
  filter(! (reporter_name %in% all_countries_to_remove))

all_rca_tibbles_binded_wo_removing_countries <- all_rca_tibbles_binded %>% 
  filter(! (reporter_name %in% all_countries_to_remove))

print(all_countries_to_remove)
```
Scaling Data to sum to 100
```{r}
countries <- as.list(unique(unlist(as.list(all_wits_tibbles_binded_wo_removing_countries$reporter_name))))
scaled_wits_tibbles <- NULL
for (country in countries) {
  print(country)
  a_df <- tibble(reporter_name = '', partner_name = '', trade_flow = '', product_group = '', indicator = '')[0,]
  for (i in 1:length(all_wits_tibbles)) {
    a_df <- a_df %>% 
      add_row(reporter_name = "", partner_name = "", trade_flow = "", product_group = "", indicator = "")
  }
    
  b1_df <- all_wits_tibbles_binded_wo_removing_countries %>% 
    filter(reporter_name == country) %>% select(!c(code)) %>% 
    bind_rows(summarise(.,
                        across(where(is.numeric), sum),
                        across(where(is.character), ~"Total"))) %>% 
    dplyr::select(!c(reporter_name, partner_name, trade_flow, product_group, indicator))
  b_df <- mapply('/', b1_df, b1_df[length(all_wits_tibbles) + 1, ])
  # View(b_df)
  
  a_df$reporter_name <- (all_wits_tibbles_binded_wo_removing_countries %>% filter(reporter_name == country))$reporter_name
  a_df$partner_name <- (all_wits_tibbles_binded_wo_removing_countries %>% filter(reporter_name == country))$partner_name
  a_df$trade_flow <- (all_wits_tibbles_binded_wo_removing_countries %>% filter(reporter_name == country))$trade_flow
  a_df$product_group <- (all_wits_tibbles_binded_wo_removing_countries %>% filter(reporter_name == country))$product_group
  a_df$indicator <- (all_wits_tibbles_binded_wo_removing_countries %>% filter(reporter_name == country))$indicator
  
  b_df <- head(b_df, -1)
  c_df <- cbind(a_df, b_df)
  
  if (i == 1) {
    scaled_wits_tibbles <- c_df
  } else {
    scaled_wits_tibbles = rbind(scaled_wits_tibbles, c_df)
  }
}

# setdiff(scaled_wits_tibbles$reporter_name, scaled_rca_tibbles$reporter_name)
scaled_wits_tibbles <- scaled_wits_tibbles %>% 
  filter(reporter_name != 'European Union')

scaled_rca_tibbles <- all_rca_tibbles_binded_wo_removing_countries %>%
  dplyr::select(-c('code')) %>% 
  arrange(reporter_name)

View(scaled_wits_tibbles)
View(scaled_rca_tibbles)
```
Multiplying the Matrices to get the weighted average
```{r}
all_numeric_wits <- scaled_wits_tibbles %>% 
  select(!c(reporter_name, partner_name, trade_flow, product_group, indicator))
all_numeric_rca <- scaled_rca_tibbles %>% 
  select(!c(reporter_name, partner_name, trade_flow, product_group, indicator))

multiplied_rca_wits <- all_numeric_wits * all_numeric_rca

all_countries <- unique(scaled_rca_tibbles$reporter_name)
list_of_countries <- c(22 * length(all_countries))
j <- 0
for (country in all_countries) {
  for (i in 1:22) {
    list_of_countries[j * 22 + i] <- country
  }; j <- j + 1
}

final_rca_dataframe_1 <- cbind(list_of_countries, multiplied_rca_wits)
colnames(final_rca_dataframe_1)[1] <- 'reporter_name'
```
Summming across product categories for final averages
```{r, warnings = FALSE}
final_rca_dataframe_2 <- final_rca_dataframe_1 %>% 
  group_by(reporter_name) %>% 
  summarise_each(list(sum))
View(final_rca_dataframe_2)
```


# Working with Country Names <a name = "country_names"></a>
```{r, warning = FALSE}
# Countries of se_size Dataset
se_size_base <- read_csv(get_file_path('Extracting PDF Data/size_of_the_shadow_economy.csv'), show_col_types = FALSE)
colnames(se_size_base)[1] <- 'country'
se_dataset_countries <- unique(se_size_base$country)[-length(unique(se_size_base$country))]
se_dataset_countries <- data.frame(matrix(unlist(se_dataset_countries), nrow=length(se_dataset_countries), byrow=TRUE))
colnames(se_dataset_countries)[1] <- 'country'

# Countries of WDI Database
population_base <- read_csv(get_file_path('Data/WDI - Population/API_SP.POP.TOTL_DS2_en_csv_v2_61.csv'), show_col_types = FALSE)
colnames(population_base)[1] <- 'country'; colnames(population_base)[2] <- 'code'
wdi_countries_and_codes <- population_base %>% select('country', 'code')

# Creating Correction Dataframe Pt. 1
merge_1 <- merge(wdi_countries_and_codes, se_dataset_countries, by = c('country'), all = TRUE)

# Countries of wa_rca Dataset
named_country_wca_list_raw <- scan(get_file_path('Extracting PDF Data/country_name_changes_wca_dataset.txt'), what="", sep="\n")
named_country_wca_list <- strsplit(named_country_wca_list_raw, "[[:space:]]->[[:space:]]")
names(named_country_wca_list) <- sapply(named_country_wca_list, `[[`, 1)
named_country_wca_list <- lapply(named_country_wca_list, `[`, -1)

# Fixing the names of the wa_rca dataset
final_rca_dataframe_3 <- final_rca_dataframe_2
final_rca_dataframe_3$reporter_name <- lapply(final_rca_dataframe_3$reporter_name, function(name) { ifelse(name %in% names(named_country_wca_list), named_country_wca_list[name], name) } )
final_rca_dataframe_3 <- final_rca_dataframe_3 %>% 
  rename('country' = 'reporter_name') %>% 
  arrange(country)
final_rca_dataframe_3 <- as.data.frame(lapply(final_rca_dataframe_3, unlist))

# Getting Updated wa_rca Countries
wa_rca_countries <- unique(final_rca_dataframe_3$country)
wa_rca_countries <- data.frame(matrix(unlist(wa_rca_countries), nrow=length(wa_rca_countries), byrow=TRUE))
colnames(wa_rca_countries)[1] <- 'country'

# Creating Correction Dataframe Pt. 2
merge_2 <- merge(merge_1, wa_rca_countries, by = c('country'), all = TRUE)

# Perfecting the wa_rca Dataset
final_rca_dataframe_4 <- merge(final_rca_dataframe_3, merge_2, by = c('country'), all.x = TRUE)
final_rca_dataframe_4 <- final_rca_dataframe_4 %>% select(country, code, 'X1988':'X2022')
colnames(final_rca_dataframe_4)[-1:-2] <- as.numeric(1988:2022)
final_rca_dataframe_4 <- final_rca_dataframe_4 %>% 
  filter(!is.na(code))

# IMF Countries Dataset
named_country_imf_list_raw <- scan(get_file_path('Extracting PDF Data/country_name_changes_imf_dataset.txt'), what="", sep="\n")
named_country_imf_list <- strsplit(named_country_imf_list_raw, "[[:space:]]->[[:space:]]")
names(named_country_imf_list) <- sapply(named_country_imf_list, `[[`, 1)
named_country_imf_list <- lapply(named_country_imf_list, `[`, -1)

all_government_revenue_base <- read_csv(get_file_path('Data/IMF - World Revenue/dataset_2026-03-23T17_40_40.193148454Z_DEFAULT_INTEGRATION_IMF.FAD_WORLD_3.0.1.csv'), show_col_types = FALSE)
all_government_revenue_base <- all_government_revenue_base %>% 
  select( c(c('COUNTRY', 'INDICATOR'), as.character(as.list(1991:2015))) )
colnames(all_government_revenue_base)[1] <- 'country'; colnames(all_government_revenue_base)[2] <- 'indicator'
all_government_revenue_base$country  <- lapply(all_government_revenue_base$country, function(name) { ifelse(name %in% names(named_country_imf_list), named_country_imf_list[name], name) } )
all_government_revenue_base <- all_government_revenue_base %>% arrange(country)
all_government_revenue_base <- as.data.frame(lapply(all_government_revenue_base, unlist))
all_government_revenue_base <- all_government_revenue_base %>% select(country, indicator, 'X1991':'X2015')
colnames(all_government_revenue_base)[-1:-2] <- as.numeric(1991:2015)

imf_countries <- unique(all_government_revenue_base$country)
imf_countries <- data.frame(matrix(unlist(imf_countries), nrow=length(imf_countries), byrow=TRUE))
colnames(imf_countries)[1] <- 'country'

merge_3 <- merge(merge_2, imf_countries, by = c('country'), all = TRUE)

all_government_revenue_base <- merge(all_government_revenue_base, merge_3, by = c('country'), all.x = TRUE)
all_government_revenue_base <- all_government_revenue_base %>% 
  filter(!is.na(code)) %>% 
  select(country, code, indicator, '1991':'2015')


# Fixing the se_size Dataset
se_size_base <- merge(se_size_base, merge_2, by = c('country'), all.x = TRUE)
se_size_base <- se_size_base %>% 
  select(country, code, '1991':'2015') %>% 
  filter(country != 'Av. over countries')

countries_to_keep <- unique(se_size_base$country)
```
Note: an analysis of names was not done for the Heritage Foundation Data, that could add observations

# Changing the Strucutre of the Data to Panel <a name = "panel"></a>
### Dependent Variable <a name = 'dep_var'></a>
```{r, results = 'hide'}
# SE Size
se_size_base <- read_csv(get_file_path('Extracting PDF Data/size_of_the_shadow_economy-adjusted.csv'), show_col_types = FALSE)
se_size_base <- se_size_base %>% select(!c('Av. over years'))
se_size = pivot_longer(se_size_base, cols = as.character(1991:2015), names_to = "year", values_to = 'se_size')
```

### Preliminaries <a name = 'pre_var'></a>
```{r, results = 'hide'}
# Population (for per capita measures)
pivot_wdi <- function(csv_path, values_to) {
  wdi_base <- read_csv(get_file_path(csv_path), show_col_types = FALSE)
  wdi_base <- wdi_base[, -(length(wdi_base) - 1)]
  wdi = pivot_longer(wdi_base, cols = as.character(1960:2024), names_to = "year", values_to = values_to)
  wdi <- wdi %>% select('country', 'year', 'code', values_to)
  return(wdi)
}
pivot_imf <- function(imf_base, values_to) {
  imf = pivot_longer(imf_base, cols = as.character(1980:2024), names_to = "year", values_to = values_to)
  imf <- imf %>% select('country', 'year', 'code', values_to)
  return(imf)
}

# Population
population <- pivot_wdi('Data/WDI - Population/API_SP.POP.TOTL_DS2_en_csv_v2_61-adjusted.csv', 'population')

# Taxes
# Tax Revenue Values
tax_revenues_base <- read_csv(get_file_path('Data/IMF - World Revenue/dataset_2026-03-23T17_40_40.193148454Z_DEFAULT_INTEGRATION_IMF.FAD_WORLD_3.0.1-adjusted.csv'), show_col_types = FALSE)
tax_revenues_base <- tax_revenues_base %>% select('country', 'code', 'indicator' = 'INDICATOR', as.character(1980:2024))

# Exports and Imports
# exports_with_per_cap <- merge(exports, population %>% select(-c('country')), 
#                               by = c('code', 'year'), all.x = TRUE)
# exports_with_per_cap <- exports_with_per_cap %>% 
#   mutate(exports_per_cap = exports / population)
```

### Independent Variables <a name = 'indep_var'></a>
```{r}
# Tariff Rate
tariff_rate <- pivot_wdi('Data/WDI - Tariff Rate, Applied, Weighted Mean, All Products/API_TM.TAX.MRCH.WM.AR.ZS_DS2_en_csv_v2_440-adjusted.csv', 'applied_tariff_rate')

# Trade Taxes
trade_taxes <- pivot_imf(tax_revenues_base %>% filter(indicator == 'Taxes on international trade and transactions, Percent of GDP'), 'trade_tax')

# WA RCA
wa_rca <- pivot_longer(final_rca_dataframe_4, cols = as.character(1988:2022), names_to = "year", values_to = "wa_rca")

# Imports Unit Value Index
imports_unit_values <- pivot_wdi('Data/WDI - Import Unit Value Index/API_TM.UVI.MRCH.XD.WD_DS2_en_csv_v2_10710-adjusted.csv', 'import_uvi')
imports_unit_values <- imports_unit_values %>% 
  mutate(import_uvi_lag = Lag(import_uvi, shift = 1), import_uvi_growth_rate = 100 * (import_uvi - import_uvi_lag) / import_uvi_lag) %>% 
  select(-c('import_uvi_lag'))

# Foreign Direct Investment
fdi <- pivot_wdi('Data/WDI - FDI/API_BX.KLT.DINV.WD.GD.ZS_DS2_en_csv_v2_115540-adjusted.csv', 'fdi')

# Average Time to Clear Exports
export_clearance_time <- pivot_wdi('Data/WDI - Average Time to Clear Exports Through Customs (days)/API_IC.CUS.DURS.EX_DS2_en_csv_v2_9141-adjusted.csv', 'export_clearance_days')
# View(export_clearance_time)

sanctions_init <- read_csv('/Users/alex/Documents/School/Research/Trade and the Shadow Economy/Data Analysis/GSDB/GSDB_Sploded_Corrected.csv', show_col_types = F)
```

### Controls <a name = 'con_var'></a>
```{r}
# Index of Economic Freedom (Tax Burden)
econ_freedom <- read_csv(get_file_path('Data/Index of Economic Freedom/heritage-index-of-economic-freedom-2026-03-12_2236-adjusted.csv'), show_col_types = FALSE)
colnames(econ_freedom)[2] <- 'year'
for (i in 1:length(colnames(econ_freedom))) {
  colnames(econ_freedom)[i] <- tolower(gsub(' ', '_', colnames(econ_freedom)[i]))
}
econ_freedom <- econ_freedom %>% 
  arrange(country, year) %>% 
  select('country', 'year', 'code', overall_score:financial_freedom)

# Other Tax Variables
sales_taxes <- pivot_imf(tax_revenues_base %>% filter(indicator == 'Sales taxes, Percent of GDP'), 'sales_tax')
social_contributions <- pivot_imf(tax_revenues_base %>% filter(indicator == 'Social security contributions, Percent of GDP'), 'social_contributions')
income_taxes <- pivot_imf(tax_revenues_base %>% filter(indicator == 'Taxes on income, profits, and capital gains, Percent of GDP'), 'income_tax')
property_taxes <- pivot_imf(tax_revenues_base %>% filter(indicator == 'Taxes on property, Percent of GDP'), 'property_tax')

# CPI
cpi <- pivot_wdi('Data/WDI - CPI/API_FP.CPI.TOTL.ZG_DS2_en_csv_v2_287-adjusted.csv', 'cpi')
deflator_init <- pivot_wdi('Data/WDI - GDP Deflator Mixed Base Years/API_NY.GDP.DEFL.ZS_DS2_en_csv_v2_8603-adjusted.csv', 'inflation')

# WGI
government_effectiveness <- pivot_wdi('Data/WDI - WGI Government Effectiveness/API_GE.EST_DS2_en_csv_v2_4300-adjusted.csv', 'gov_eff')
rule_of_law <- pivot_wdi('Data/WDI - WGI Rule of Law/API_RL.EST_DS2_en_csv_v2_5814-adjusted.csv', 'rule_law')
regulatory_quality <- pivot_wdi('Data/WDI - WGI Regulatory Quality/API_RQ.EST_DS2_en_csv_v2_8225-adjusted.csv', 'reg_qua')
control_of_corruption <- pivot_wdi('Data/WDI - WGI Control of Corruption/API_CC.EST_DS2_en_csv_v2_4455-adjusted.csv', 'cont_corr')

# Size of Agricultural Sector
agri <- pivot_wdi('Data/WDI - Size of Agricultural Sector/API_NV.AGR.TOTL.ZS_DS2_en_csv_v2_1401-adjusted.csv', 'size_agri')
```
Moving the Deflator to have 2015 as its base year
```{r}
deflator_2015 <- deflator_init %>% 
  filter(year == 1995) %>% 
  mutate(freq = 65) %>% uncount(freq) %>% 
  mutate(year = rep(c(1960:2024), 217)) %>% 
  select(c('country', 'year', 'inflation'))

deflator <- merge(deflator_init, deflator_2015, by = c('country', 'year'), all.x = T, all.y = F)
deflator <- deflator %>% mutate(inflation = inflation.x / inflation.y * 100) %>% select(-c('inflation.x', 'inflation.y'))
```

### Messing with Export Clearance Time
```{r}
grouped_statistics <- export_clearance_time %>% 
  group_by(country) %>% 
  summarise(Non_NAs = n() - sum(is.na(export_clearance_days)), mean = mean(export_clearance_days, na.rm = TRUE), sd = sd(export_clearance_days, na.rm = TRUE))
View(grouped_statistics)
```

# Merging Data
```{r}
se_size_final <- se_size %>% select(country, year, se_size)

tariff_rate_final <- tariff_rate %>% select(-c('code'))
trade_taxes_final <- trade_taxes %>% select(-c('code'))
wa_rca_final <- wa_rca %>% select(-c('code'))
imports_unit_values_final <- imports_unit_values %>% select(-c('code'))
sanctions_final <- sanctions_init %>% select(country, year, export_sanction = exp, import_sanction = imp)
fdi_final <- fdi %>% select(-c('code'))

tax_burden_final <- econ_freedom %>% select('country', 'year', 'tax_burden')
sales_taxes_final <- sales_taxes %>% select(-c('code'))
social_contributions_final <- social_contributions %>% select(-c('code'))
property_taxes_final <- property_taxes %>% select(-c('code'))
income_taxes_final <- income_taxes %>% select(-c('code'))
cpi_final <- cpi %>% select(-c('code'))
deflator_final <- deflator %>% select(-c('code'))
agri_final <- agri %>% select(-c('code'))

government_effectiveness_final <- government_effectiveness %>% select(-c('code'))
rule_of_law_final <- rule_of_law %>% select(-c('code'))
regulatory_quality_final <- regulatory_quality %>% select(-c('code'))
control_of_corruption_final <- control_of_corruption %>% select(-c('code'))
```

```{r}
all_final_dfs <- list(se_size_final, tariff_rate_final, trade_taxes_final, wa_rca_final, imports_unit_values_final, fdi_final, 
                      tax_burden_final, sales_taxes_final, social_contributions_final, property_taxes_final, income_taxes_final, cpi_final, deflator_final, government_effectiveness_final, rule_of_law_final, regulatory_quality_final, control_of_corruption_final, agri_final)
trade_and_the_se_df <- merge(all_final_dfs[1], all_final_dfs[2], by = c('country', 'year'))
for (i in 3:length(all_final_dfs)) {
  trade_and_the_se_df <- merge(trade_and_the_se_df, all_final_dfs[i], by = c('country', 'year'))
}
trade_and_the_se_df <- merge(trade_and_the_se_df, sanctions_final, by = c('country', 'year'), all.x = T)
trade_and_the_se_df <- trade_and_the_se_df %>% mutate(import_sanction = replace_na(import_sanction, 0), export_sanction = replace_na(export_sanction, 0))

View(trade_and_the_se_df)
```

# Exporting the Dataset <a name = 'exporting'></a>
```{r}
write.csv(trade_and_the_se_df, file = get_file_path('trade_and_the_se_2.csv'), row.names = F)
```




